$Z^\prime$ mass limits and the naturalness of supersymmetry

### 2015-03-06 paper/e6ssm-tuning-paper.tex
Added O(t^2) m_S^2 coefficient, think all algebraic errors have been accounted for in my simplification but it would be a good idea to check this numerically if there is time

%   For this we also fix [what we fix + explain different choices to
%   before and their impact].
\begin{figure}[h]
\begin{center}
\resizebox{!}{10cm}{%
\includegraphics{all_models_tuning_vs_higgs.png}}
\caption{Scatter plot of fine tuning vs lightest Higgs mass for the
  MSSM (green, bottom band), E$_6$SSM with $M_{Z^\prime} = 2.5$ TeV (blue, middle band) and
  E$_6$SSM with $M_{Z^\prime} = 4.5$ TeV (red, top band).}
\label{Fig:e6ssmvsmssm}
\end{center}
\end{figure}
In Fig \ref{Fig:e6ssmvsmssm} results from the scan are plotted showing
the tuning for each case against the lightest Higgs mass.  As expected
the dependence on the Higgs mass is now quite weak, while the minimum
tuning in the model for the E$_6$SSM is increased by the mass of the
$Z^\prime$ boson.  So in the case of a very low cutoff the tuning
required to get a 125 GeV Higgs is not so large.  However the tuning
from the $Z^\prime$ mass appears already at tree level and is
therefore not suppressed when the cutoff scale is low. In our scan we
find that, for the points satisfying the current limit on the mass of
the $Z^\prime$ boson and having an approximately 125 GeV Higgs, the
minimum fine tuning that can be achieved is
$\Delta_{\textrm{min}}\approx 121$. If run II of the LHC further
pushes up the limit on the $Z^\prime$ mass to be above $4.5$ TeV then
the fine tuning in the model will be greater than at least
$\Delta_{\textrm{min}}\approx 394$ for a Higgs mass between $124.5$
GeV and $125.5$ GeV.

@@

In the top panel one can see that the MSSM BM1 tuning (green curve) 
steadily climbs as the cutoff scale is increased, as one would expect
when the tuning originates from large soft masses entering from the
RGEs. The panel on the middle left confirms this, showing that the
largest tuning contributions come from $\Delta_{A_t}$ and
$\Delta_{m_{H_u}^2}$ with the former being the larger sensitivity
until $M_X\approx 10^8$ GeV at which point $\Delta_{m_{H_u}^2}$ takes
over, leading to the small kink in overall tuning which can be seen in
the green curve in the top panel. In this case we have chosen a
point with large mixing, which is known to reduce the MSSM tuning.  We
found this does not eliminate the tuning as there is still a strong
sensitivity to $A_t$, but we did find that increasing $A_t$ lead less
fine tuning overall for the points we looked at.

@@

b_{m_S^2}^{(2)}&=.\label{eq:USSMms2Ot2Coeff}

>>>>

%   For this we also fix [what we fix + explain different choices to
%   before and their impact].
\begin{figure}[h]
\begin{center}
\resizebox{!}{10cm}{%
\includegraphics{all_models_tuning_vs_higgs.png}}
\caption{Scatter plot of fine tuning vs lightest Higgs mass for the
  MSSM (green, bottom band), E$_6$SSM with $M_{Z^\prime} = 2.5$ TeV (blue, middle band) and
  E$_6$SSM with $M_{Z^\prime} = 4.5$ TeV (red, top band).}
\label{Fig:e6ssmvsmssm}
\end{center}
\end{figure}
In Fig \ref{Fig:e6ssmvsmssm} results from the scan are plotted showing
the tuning for each case against the lightest Higgs mass.  As expected
the dependence on the Higgs mass is now quite weak, while the minimum
tuning in the model for the E$_6$SSM is increased by the mass of the
$Z^\prime$ boson.  So in the case of a very low cutoff the tuning
required to get a 125 GeV Higgs is not so large.  However the tuning
from the $Z^\prime$ mass appears already at tree level and is
therefore not suppressed when the cutoff scale is low. In our scan we find that, for the points satisfying the current limit on the mass of the $Z^\prime$ boson and having an approximately 125 GeV Higgs, the minimum fine tuning that can be achieved is 
$\Delta_{\textrm{min}}\approx 121$.

If run II of the LHC further pushes up the limit on the $Z^\prime$
mass to be above $4.5$ TeV then the fine tuning in the model will be
greater than at least $\Delta_{\textrm{min}}\approx 394$ for a Higgs mass between $124.5$ GeV and $125.5$ GeV.

@@

In the top panel one can see that the MSSM BM1 tuning 
steadily climbs as the cutoff scale is increased, as one would expect
when the tuning originates from large soft masses entering from the
RGEs. The panel on the middle left confirms this, showing that the
largest tuning contributions come from $\Delta_{A_t}$ and
$\Delta_{m_{H_u}^2}$ with the former being the larger sensitivity
until $M_X\approx 10^8$ GeV at which point $\Delta_{m_{H_u}^2}$ takes
over, leading to the small kink in overall tuning which can be seen in
the green curve in the top panel. In this case we have chosen a
point with large mixing, which is known to reduce the MSSM tuning.  We
found this does not eliminate the tuning as there is still a strong
sensitivity to $A_t$, but we did find that increasing $A_t$ lead less
fine tuning overall for the points we looked at.

@@

b_{m_S^2}^{(2)}&=8\sum_{i=1}^3\left [ 2\lambda_i^4\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2\right )+4\lambda_i^2a_{\lambda_i}^2 +3\kappa_i^4\left ( m_S^2+m_{Di}^2+m_{\overline{D}i}^2\right )+6\kappa_i^2a_{\kappa_i}^2\right ]\nonumber\\
&{}+8\sum_{i=1}^3\sum_{j=1}^3\left [ \lambda_i^2\lambda_j^2\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_{H_j^d}^2+m_{H_j^u}^2+2m_S^2\right )+\left ( \lambda_i a_{\lambda_j}+\lambda_ja_{\lambda_i}\right )^2\right ]\nonumber\\
&{}+24\sum_{i=1}^3\sum_{j=1}^3\left [ \lambda_i^2\kappa_j^2\left ( m_{H_i^d}^2+m_{H_i^u}^2+2m_S^2+m_{Di}^2+m_{\overline{D}i}^2\right )+\left ( \lambda_ia_{\kappa_j}+\kappa_ja_{\lambda_i}\right )^2\right ]\nonumber\\
&{}+18\sum_{i=1}^3\sum_{j=1}^3\left [ \kappa_i^2\kappa_j^2\left ( 2m_S^2+m_{Di}^2+m_{\overline{D}i}^2+m_{Dj}^2+m_{\overline{D}j}^2\right )+\left ( \kappa_ia_{\kappa_j}+\kappa_ja_{\kappa_i}\right )^2\right ]\nonumber\\
&{}+12\lambda^2y_t^2\left ( 2m_{H_u}^2+m_{H_d}^2+m_S^2+m_{Q3}^2+m_{u3}^2\right )+12\lambda^2y_b^2\left ( m_{H_u}^2+2m_{H_d}^2+m_S^2\right.\nonumber\\
&{}\left.+m_{Q3}^2+m_{d3}^2\right )+4\lambda^2y_\tau^2\left ( 2m_{H_d}^2+m_{H_u}^2+m_S^2+m_{L3}^2+m_{e3}^2\right )+12\left ( \lambda a_t+y_ta_{\lambda}\right )^2\nonumber\\
&{}+12\left ( \lambda a_b+y_ba_{\lambda}\right )^2+4\left ( \lambda a_\tau+y_\tau a_{\lambda}\right )^2-32g_3^2\sum_{i=1}^3\left [ \kappa_i^2\left ( m_S^2+m_{Di}^2+m_{\overline{D}i}^2+2M_3^2\right )\right.\nonumber\\
&{}\left.+a_{\kappa_i}^2-2\kappa_ia_{\kappa_i}M_3\right ]-12g_2^2\sum_{i=1}^3\left [ \lambda_i^2\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2+2M_2^2\right )+a_{\lambda_i}^2-2\lambda_i a_{\lambda_i}M_2\right ]\nonumber\\
&{}-\frac{4}{5}g_1^2\sum_{i=1}^3\Big [ 3\lambda_i^2\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2+2M_1^2\right )+3a_{\lambda_i}^2-6\lambda_i a_{\lambda_i}M_1\nonumber\\
&{}+2\kappa_i^2\left ( m_S^2+m_{Di}^2+m_{\overline{D}i}^2+2M_1^2\right )+2a_{\kappa_i}^2-4\kappa_i a_{\kappa_i}M_1\Big ]\nonumber\\
&{}+2g_1'^2\sum_{i=1}^3\Big [ -4\lambda_i^2\left ( Q_1^2+Q_2^2+Q_S^2\right )\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2+2M_1'^2\right )\nonumber\\
&{}+2\lambda_i^2\left ( Q_1+Q_2+Q_S\right )\left ( Q_Sm_{H_i^d}^2+Q_Sm_{H_i^u}^2+Q_Sm_S^2+\Sigma_1'\right )-4\left ( Q_1^2+Q_2^2+Q_S^2\right )\times\nonumber\\
&{}\times\left ( a_{\lambda_i}^2-2\lambda_i a_{\lambda_i}M_1'\right )+2Q_Sa_{\lambda_i}^2\left ( Q_1+Q_2+Q_S\right )-6\kappa_i^2\left ( Q_S^2+Q_D^2+Q_{\overline{D}}^2\right )\times\nonumber\\
&{}\times\left ( m_S^2+m_{Di}^2+m_{\overline{D}i}^2+2M_1'^2\right )+3\kappa_i^2\left ( Q_S+Q_D+Q_{\overline{D}}\right )\left ( Q_Sm_S^2+Q_Sm_{Di}^2+Q_Sm_{\overline{D}i}^2+\Sigma_1'\right )\nonumber\\
&{}-6\left ( Q_S^2+Q_D^2+Q_{\overline{D}}^2\right )\left ( a_{\kappa_i}^2-2\kappa_i a_{\kappa_i}M_1'\right )+3Q_Sa_{\kappa_i}^2\left ( Q_S+Q_D+Q_{\overline{D}}\right )\Big ]\nonumber\\
&{}+12Q_Sg_1'^2y_t^2\left ( Q_2+Q_Q+Q_u\right )\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2\right )+12Q_Sg_1'^2a_t^2\left ( Q_2+Q_Q+Q_u\right )\nonumber\\
&{}+12Q_Sg_1'^2y_b^2\left ( Q_1+Q_Q+Q_d\right )\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2\right )+12Q_Sg_1'^2a_b^2\left ( Q_1+Q_Q+Q_d\right )\nonumber\\
&{}+4Q_Sg_1'^2y_\tau^2\left ( Q_1+Q_L+Q_e\right )\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2\right )+4Q_Sg_1'^2a_\tau^2\left ( Q_1+Q_L+Q_e\right )\nonumber\\
&{}-96Q_Sg_3^2g_1'^2M_3^2\left ( 2Q_Q+Q_u+Q_d+Q_D+Q_{\overline{D}}\right )-12Q_Sg_2^2g_1'^2M_2^2\big ( 9Q_Q+3Q_L+3Q_1\nonumber\\
&{}+3Q_2+Q_{\overline{H'}}+Q_{H'}\big )-\frac{6}{5}Q_Sg_1^2g_1'^2\Big [ 2M_1^2\big ( 2Q_d+2Q_{\overline{D}}+2Q_D+6Q_e+3Q_1+3Q_2+Q_{\overline{H'}}\nonumber\\
&{}+Q_{H'}+3Q_L+Q_Q+8Q_u\big )-\Sigma_1\big ( 3Q_d+3Q_{\overline{D}}-3Q_D+3Q_e-3Q_1+3Q_2+Q_{\overline{H'}}-Q_{H'}\nonumber\\
&{}-3Q_L+3Q_Q-6Q_u\big )\Big ]-4Q_Sg_1'^4\Big [ 2M_1'^2\big ( 9Q_d^3+9Q_{\overline{D}}^3+9Q_D^3+3Q_e^3+6Q_1^3+6Q_2^3+2Q_{\overline{H'}}^3\nonumber\\
&{}+2Q_{H'}^3+6Q_L^3+18Q_Q^3+3Q_S^3+9Q_u^3\big )+\left ( 6Q_SM_1'^2-\Sigma_1'\right )\Sigma_Q\Big ].\label{eq:USSMms2Ot2Coeff}
